AP/PA Tables ITHIM Global

### 2021-05-18 summary_tables_PA_AP.Rmd
Adding one PA table

@@

<!-- # Descriptive tables of Individual-level Physical activity (MMETs) -->

<!-- ```{r, message=FALSE, warning=FALSE, echo=FALSE} -->
<!-- for (x in 1: length(cities)) -->
<!-- { -->
<!--   names(io[[cities[x]]]$outcomes$mmets)[5:10]<-c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen") -->
<!--   data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, baseline:bus_scen, factor_key=TRUE) -->
<!--   summary<- as.data.frame(data_long %>% group_by(scenario) %>% summarise('mean'=mean(mmet),'5th'=quantile(mmet, 0.05),'50th'=quantile(mmet, 0.5),'95th'=quantile(mmet, 0.9))) -->
<!--   summary<- cbind(summary$scenario ,round(summary[,2:5], digits=1)) -->
<!--   names(summary)[1]<-"Scenario" -->
<!--   print(kable(summary, caption= cities[x])) -->

>>>>

}
```
# Descriptive tables of Individual-level Physical activity (MMETs)

```{r, message=FALSE, warning=FALSE, echo=FALSE}
for (x in 1:length(cities)) {
  names(io[[cities[x]]]$outcomes$mmets)[5:10] <- c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, baseline:bus_scen, factor_key = TRUE)
  summary <- as.data.frame(data_long %>% group_by(scenario) %>% 
                             summarise('mean' = mean(mmet),
                                       '5th' = quantile(mmet, 0.05),
                                       '50th' = quantile(mmet, 0.5),
                                       '95th' = quantile(mmet, 0.9)))
  summary <- cbind(summary$scenario ,round(summary[,2:5], digits = 1))
  names(summary)[1] <- "Scenario"
  print(kable(summary, caption = cities[x]))

@@

# Descriptive table for Physical Activity (MMETs)
```{r, message=FALSE, warning=FALSE, echo=FALSE}

  td <- round(colMeans(io[[city]]$outcomes$mmets[,5:10], na.rm = T), 1) %>% as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', city)
